\documentclass{article}
\usepackage{enumitem}
\usepackage{amsmath}
\begin{document}

\title{Chapter 27: Principles of Inheritance and Variation}
\date{}
\maketitle

\begin{enumerate}[label=Q\arabic*.]

\item In a dihybrid cross AaBb $\times$ AaBb, the phenotypic ratio is 9:3:3:1. This ratio would change to 9:3:4 if:
\\(A) Both genes are linked
\\(B) Gene B is epistatic to gene A (recessive epistasis)
\\(C) Incomplete dominance occurs in both genes
\\(D) Crossing over occurs between the two genes

\item A woman with normal vision (carrier) marries a color-blind man. What is the probability of their sons being color-blind?
\\(A) 0\%
\\(B) 25\%
\\(C) 50\%
\\(D) 100\%

\item In codominance (e.g., blood group AB), the phenotype of the heterozygote is:
\\(A) Intermediate between two parents
\\(B) Both alleles are expressed simultaneously and independently
\\(C) One allele is completely masked by the other
\\(D) A new phenotype not seen in either parent

\item Which of the following represents a trihybrid cross yielding 27:9:9:9:3:3:3:1 ratio?
\\(A) AaBb $\times$ AaBb
\\(B) AaBbCc $\times$ AaBbCc (with all genes independently assorting)
\\(C) AABB $\times$ aabb
\\(D) AaBbCc $\times$ AaBbcc

\item Assertion: Pleiotropy is the phenomenon where one gene affects multiple phenotypic traits.\\
Reason: The gene for phenylalanine hydroxylase when mutated (PKU) affects pigmentation, neurological function, and other traits.
\\(A) Both true, Reason is correct explanation
\\(B) Both true, Reason is not correct explanation
\\(C) Assertion true, Reason false
\\(D) Assertion false, Reason true

\item A test cross is performed between a tall pea plant (unknown genotype) and a short plant. If all offspring are tall, the genotype of the tall plant is:
\\(A) Tt
\\(B) TT
\\(C) tt
\\(D) Cannot be determined

\item In humans, sex is determined by the sex chromosomes. The sex of the offspring is determined by:
\\(A) The mother's X chromosome contributed
\\(B) The father's sex chromosome (X or Y) in the sperm
\\(C) Maternal hormones during pregnancy
\\(D) Equal contribution of both parents

\item A family has 4 daughters. What is the probability that the 5th child will be a son?
\\(A) 100\% (since 4 daughters already born)
\\(B) 75\%
\\(C) 50\% (each birth is independent)
\\(D) 25\%

\item Haemophilia A is caused by deficiency of clotting factor VIII. A carrier female (X$^H$X$^h$) $\times$ normal male (X$^H$Y). What proportion of daughters will be carriers?
\\(A) 0\%
\\(B) 25\%
\\(C) 50\%
\\(D) 100\%

\item Chromosomal theory of inheritance was proposed by:
\\(A) Gregor Mendel
\\(B) Sutton and Boveri
\\(C) Thomas Hunt Morgan
\\(D) Hugo de Vries

\item In Morgan's experiments with \textit{Drosophila}, recombination frequency between two genes is 10\%. This means the genes are:
\\(A) 10 Morgans (centimorgans) apart on the same chromosome
\\(B) On different chromosomes
\\(C) In repulsion configuration only
\\(D) Involved in epistasis

\item Down syndrome (Trisomy 21) most commonly arises due to:
\\(A) Deletion of chromosome 21
\\(B) Non-disjunction of chromosome 21 during meiosis, usually in maternal meiosis I
\\(C) Translocation of chromosome 21 to chromosome 14
\\(D) Point mutation in chromosome 21

\item The chi-square ($\chi^2$) test is used in genetics to:
\\(A) Calculate allele frequencies
\\(B) Determine if observed phenotypic ratios deviate significantly from expected Mendelian ratios
\\(C) Map chromosome distances
\\(D) Identify mutations in DNA sequences

\item Match the following genetic phenomena with examples:\\
1. Codominance $\rightarrow$ (a) Blood group AB (both A and B antigens expressed)\\
2. Incomplete dominance $\rightarrow$ (b) Pink flower in snapdragon (Antirrhinum)\\
3. Epistasis $\rightarrow$ (c) 9:7 ratio in two-gene cross\\
4. Polygenic inheritance $\rightarrow$ (d) Human skin color (continuous variation)
\\(A) 1-a, 2-b, 3-c, 4-d
\\(B) 1-b, 2-a, 3-d, 4-c
\\(C) 1-c, 2-d, 3-a, 4-b
\\(D) 1-d, 2-c, 3-b, 4-a

\item A man with blood group A (I$^A$i) marries a woman with blood group B (I$^B$i). Which blood groups are possible in their children?
\\(A) A and B only
\\(B) A, B, AB, and O
\\(C) AB only
\\(D) A, B, and AB only

\end{enumerate}
\end{document}
